Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-25 architecture.tex
Updated buil for proposal
Updates from ShareLaTeX

\begin{figure}
\centering
	\includegraphics[width=.5\textwidth]{figs/architecture}
\caption{Flink's Process Model.}
\end{figure}

\begin{figure}[ht]
\centering     %%% not \center
\subfigure[The Flink software stack.]{\label{fig:FlinkStack}\includegraphics[width=.5\textwidth]{figs/stack.pdf}}
\subfigure[The JobGraph is the logical view of a Flink job.]{\label{fig:JobGraph}\begin{tikzpicture}
[shorten >=1pt,node distance=1.75cm,>=stealth',initial text=, font=\tiny]
\tikzstyle{op}=[circle, draw=blue!50,very thick,fill=blue!20, text width=0.5cm]
\tikzstyle{ir}=[cylinder, cylinder uses custom fill, cylinder body fill=orange!50, cylinder end fill=orange!50, shape border rotate=90, aspect=0.35, draw, minimum size=1cm, text width=0.5cm, align=center]

\node[op] (op_1) {~~~~~~~};
\node[ir] (ir_1) [right of = op_1] {~~~~~~~};
\node[op] (op_2) [right of = ir_1] {~~~~~~~};
\node[ir] (ir_2) [right of = op_2] {~~~~~~~};
\node[op] (op_3) [below of = op_2] {~~~~~~~};
\node[ir] (ir_3) [right of = op_3] {~~~~~~~};
\node[op] (op_4) [right of = ir_2] {~~~~~~~};
\node[op] (op_5) [right of = ir_3] {~~~~~~~};

\path[->] 	
			(op_1) 	edge node [above] {} (ir_1)
			(ir_1) 	edge node [above] {} (op_2)
			(op_2) 	edge node [above] {} (ir_2)
			(ir_2) 	edge node [above] {} (op_4)
			(op_3) 	edge node [above] {} (ir_3)
			(ir_3) 	edge node [above] {} (op_4)
			(ir_3) 	edge node [above] {} (op_5)
			;
\end{tikzpicture}}
\caption{Apache Flink architecture.}
\end{figure}

>>>>

\begin{figure}
\centering
	\includegraphics[width=.75\textwidth]{figs/process_model_updated}
\caption{Flink's Process Model.}
\end{figure}

\begin{figure}[ht]
\centering     %%% not \center
\label{fig:FlinkStack}
\includegraphics[width=.5\textwidth]{figs/stack.pdf}
% \subfigure[The JobGraph is the logical view of a Flink job.]{\label{fig:JobGraph}\begin{tikzpicture}
% [shorten >=1pt,node distance=1.75cm,>=stealth',initial text=, font=\tiny]
% \tikzstyle{op}=[circle, draw=blue!50,very thick,fill=blue!20, text width=0.5cm]
% \tikzstyle{ir}=[cylinder, cylinder uses custom fill, cylinder body fill=orange!50, cylinder end fill=orange!50, shape border rotate=90, aspect=0.35, draw, minimum size=1cm, text width=0.5cm, align=center]

% \node[op] (op_1) {~~~~~~~};
% \node[ir] (ir_1) [right of = op_1] {~~~~~~~};
% \node[op] (op_2) [right of = ir_1] {~~~~~~~};
% \node[ir] (ir_2) [right of = op_2] {~~~~~~~};
% \node[op] (op_3) [below of = op_2] {~~~~~~~};
% \node[ir] (ir_3) [right of = op_3] {~~~~~~~};
% \node[op] (op_4) [right of = ir_2] {~~~~~~~};
% \node[op] (op_5) [right of = ir_3] {~~~~~~~};

% \path[->] 	
% 			(op_1) 	edge node [above] {} (ir_1)
% 			(ir_1) 	edge node [above] {} (op_2)
% 			(op_2) 	edge node [above] {} (ir_2)
% 			(ir_2) 	edge node [above] {} (op_4)
% 			(op_3) 	edge node [above] {} (ir_3)
% 			(ir_3) 	edge node [above] {} (op_4)
% 			(ir_3) 	edge node [above] {} (op_5)
% 			;
% \end{tikzpicture}}
\caption{Flink's software stack.}
\end{figure}
